---
title: "Portfolio7"
author: "Fei Xie"
date: "5/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#The changing trajectories of CO2 emission and forest land
Now we use CO2 and Forest data from 1990 to 2015 to see the changing trajectories of CO2 emission and forest land. 

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(dplyr)
library(rworldmap)
```

```{r load-data, message=FALSE}
CO2 <- read_csv("data/co2_emissions_tonnes_per_person.csv", na = c("",".","NA"))
Forest <- read_csv("data/forest_land_total_area_ha.csv", na = c("",".","NA"))
```

###Merge longitudinal data points into one column

```{r merge-columns}
CO2_long <- gather(CO2, year, data, -country)
library(countrycode)
CO2_long$continent <- countrycode(sourcevar = CO2_long$country,
            origin = "country.name",
            destination = "continent")

forest_long <- gather(Forest, year, data, -country)
forest_long$continent <- countrycode(sourcevar = forest_long$country,
            origin = "country.name",
            destination = "continent")
```

###Merge the forest and CO2 data sets
```{r merge-data}
#add labels
CO2_long$type <- "CO2"
forest_long$type <- "forest"
#return all rows
combined <- full_join(CO2_long, forest_long)
```


###Changing curves
```{r forest-curve}
ggplot(forest_long,
       aes(x = year,
           y = data,
           group = country))+
  geom_point(size = 1)+
  geom_line(color = "grey")+
  stat_smooth(aes(group = 1),  method = "lm", color = "Red") + 
  stat_summary(aes(group = 1),
    geom = "point", fun = mean, color = "Blue")+
  #facet_grid(.~continent)
  facet_wrap(.~continent, ncol =2 )
```

```{r CO2-curve}
ggplot(CO2_long,
       aes(x = year,
           y = data,
           group = country))+
  geom_point(size = 1)+
  geom_line(color = "grey")+
  stat_smooth(aes(group = 1),  method = "lm", color = "Red") + 
  stat_summary(aes(group = 1),
    geom = "point", fun = mean, color = "Blue")+
  #facet_grid(.~continent)
  facet_wrap(.~continent, ncol =2 )
```

From the plots above, we know that the number of forest land in each country stays from 1990 to 2015. But a few countries' CO2 emission per person increased, especially in Asia and Americas.

